Estimating Predictive Rate-Distortion Curves via Neural Variational Inference

### 2019-05-01 paper.tex
Updates from Overleaf

The information curve is shown in Figure~\ref{fig:eng-pos} (left).
In the setting of low rate and high distortion, NPRD and OCF (blue, $M=1,2,3$) show essentially identical results.
This holds true until $\operatorname{I}[Z, \future] \approx 0.7$, at which point the bounds provided by OCF deteriorate, showing the effects of overfitting.
NPRD continues to provide estimates at greater rates.

@@

Our analysis of PRD curves for natural language suggests that human language is characterized by very high and perhaps infinite statistical complexity, beyond its excess entropy. In a similar vein, \citet{dkebowski2018natural} has argued that the excess entropy of connected texts in natural language is infinite (in contrast, our result is for isolated sentences). If the statistical complexity of natural language is indeed infinite, then statistical complexity is not a useful complexity metric for characterizing natural language.

>>>>

The PRD curve is shown in Figure~\ref{fig:eng-pos} (left).
In the setting of low rate and high distortion, NPRD and OCF (blue, $M=1,2,3$) show essentially identical results.
This holds true until $\operatorname{I}[Z, \future] \approx 0.7$, at which point the bounds provided by OCF deteriorate, showing the effects of overfitting.
NPRD continues to provide estimates at greater rates.

@@

Our analysis of PRD curves for natural language suggests that human language is characterized by very high and perhaps infinite statistical complexity, beyond its excess entropy. In a similar vein, \citet{dkebowski2018natural} has argued that the excess entropy of connected texts in natural language is infinite (in contrast, our result is for isolated sentences). If the statistical complexity of natural language is indeed infinite, then statistical complexity is not sufficiently fine-grained as a complexity metric for characterizing natural language.
